pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Code and text of ERQ 3 must match

The objects we just created need to be bundled
in a \verb;pirouette; parameters structure,
together with error measurement parameters $\mathit{E}$ and
twinning parameters $\mathit{T}$. We use the default error measurement
parameters, which uses a burn-in of 10\% and the nLTT statistic to
measure the difference between phylogenies. We will not use twinning
here yet.  
All these arguments are bundled
and checked by \verb;create_pir_params;:

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lst:create_pir_params},
  caption = Calling \texttt{create\_pir\_params}
]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  error_measure_params = create_error_measure_params(),
  twinning_params = NA
)
\end{lstlisting}

@@

Creating a twinning parameter is easy, as it has sensible default settings:

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, 
  frame=single,
  label = {lst:create_twinning_params},
  caption = Create the default twinning parameters
]
twinning_params <- create_twinning_params()
\end{lstlisting}

@@

"What is the error made by BEAST2 from a phylogeny 
derived from an unknown speciation model,
when selecting the best inference model, 
in relationship to the background error?"
\richel{
  I inserted this example research question, 
  as think this is natural intermediate between the 
  previous and next/final example
}

@@

In the second step we specify we want all 
40 inference models to compete, by 
calling \verb;create_all_experiments;,
as done in listing~\ref{lst:create_all_experiments}.

We choose again to use sensible defaults for the third (the BEAST2 inference) 
and fourth (measuring the error) steps, 
as we previously did to answer the second research question.

>>>>

The objects we just created need to be bundled
in a \verb;pirouette; parameters structure,
together with error measurement parameters $\mathit{E}$ and
twinning parameters $\mathit{T}$.

We use the default error measurement
parameters, which uses a burn-in of 10\% and the nLTT statistic to
measure the difference between phylogenies. For clarity,
we create this setup explicitly here:

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lst:create_error_measure_params},
  caption = Calling \texttt{create\_error\_measure\_params}
]
error_measure_params <- create_error_measure_params(
  burn_in_fraction = 0.1, 
  error_function = get_nltt_error_function()
)
\end{lstlisting}

We will not use twinning
here yet.  
All these arguments are bundled
and checked by \verb;create_pir_params;:

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lst:create_pir_params},
  caption = Calling \texttt{create\_pir\_params}
]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  error_measure_params = error_measure_params,
  twinning_params = NA
)
\end{lstlisting}

@@

Creating a twinning parameter is easy, as it has sensible default settings.
For clarity, we explicitly show the default values of the most
important arguments:

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, 
  frame=single,
  label = {lst:create_twinning_params},
  caption = Create the default twinning parameters
]
twinning_params <- create_twinning_params(
  twin_model = "bd", 
  method = "random_tree"
)
\end{lstlisting}

\richel{
  I would enjoy being able to write ...
}
\begin{lstlisting}
  twinning_params <- create_twinning_params(
    tree_prior = create_bd_tree_prior(),
    ...
  )
)
\end{lstlisting}
\richel{
  ... as that would connect the tree priors more
}

@@

"What is the error made by BEAST2 from a phylogeny 
derived from an unknown speciation model,
when selecting the best inference model, 
in relationship to the background error?"

@@

We agin specify we want all 40 inference models to compete, 
by calling \verb;create_all_experiments;,
as done in listing~\ref{lst:create_all_experiments}.

We again pick to use the default setup to measure the error,
as shown in listing~\ref{lst:create_error_measure_params}.
